\subsection{{Spotify Listening Data Analytics Dashboard} \href{https://app.powerbi.com/view?r=eyJrIjoiOGQ3OGJkZWMtY2M0Mi00M2M2LTlhNGItOTliZTdmYjk3NDYxIiwidCI6IjY4ODk2ZGVkLWViZWQtNGE4My05YTQ3LTM2ZTA2M2VjMTVhYyJ9}{[link]}}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Built an interactive dashboard to analyze user listening behavior, track engagement, and playback patterns.
    \item Delivered insights into user actions such as skips, play reasons, and shuffle usage across various platforms.
    \item Identified peak listening hours and engagement trends using time-based session analysis.
\end{zitemize}

\subsection{{Employee Attrition Prediction for HR Analytics} \href{https://colab.research.google.com/github/HarshRaj00789/Predicting-Employee-Attrition-A-Data-Driven-Approach-for-HR-Optimization/blob/main/Predicting_Employee_Attrition_A_Data_Driven_Approach_for_HR_Optimization.ipynb?authuser=1}{[link]}}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Built models to forecast attrition and inform HR strategies.
    \item Conducted exploratory data analysis and visualized trends influencing attrition such as job role, work environment, and tenure.
    \item Improved model performance through hyperparameter tuning, enabling accurate forecasting of attrition risk.
\end{zitemize}

\subsection{{Yellow Taxi Trip Data Analysis and Visualization} \href{https://github.com/HarshRaj00789/Taxi-tip-Exploratory-data-analysis}{[link]}}
\begin{zitemize}
    \setlength\itemsep{0.4em}
    \item Analyzed NYC Yellow Taxi data to uncover trends in passenger behavior, trip characteristics, and tipping patterns.
    \item Visualized revenue, trip distances, and ride counts across time, vendor type, and geolocations to inform strategy.
    \item Delivered actionable insights through time-based and geospatial analysis for improved transportation management.
\end{zitemize}